### 2018-12-08 Sections/errors_in_quantum_networks.tex
Generalised cat state loss result

Consider an even-parity cat state, as per Eq.~(\ref{eq:cat_state_enc}). Subjecting this to a loss channel yields the mixed state,
\begin{align}
&\hat\rho_\mathrm{loss} = \mathcal{E}_\eta^\mathrm{loss}(\ket{\mathrm{cat}_+(\alpha)}\bra{\mathrm{cat}_+(\alpha)}) \nonumber\\
&= {\mathcal{N}_+}^2 [\mathcal{E}_\eta^\mathrm{loss}(\ket{\alpha}\bra{\alpha}) + \mathcal{E}_\eta^\mathrm{loss}(\ket{-\alpha}\bra{-\alpha}) \nonumber\\
&+ \mathcal{E}_\eta^\mathrm{loss}(\ket{-\alpha}\bra{\alpha}) + \mathcal{E}_\eta^\mathrm{loss}(\ket{\alpha}\bra{-\alpha})]\nonumber\\
&= {\mathcal{N}_+}^2[\ket{\eta\alpha}\bra{\eta\alpha} + \ket{-\eta\alpha}\bra{-\eta\alpha}\nonumber\\
&+e^{-2|(1-\eta)\alpha|^2}(\ket{\eta\alpha}\bra{-\eta\alpha}+\ket{-\eta\alpha}\bra{\eta\alpha})].
\end{align}
Now it's evident that the off-diagonal terms (i.e those representing coherence) accumulate a factor of,
\begin{align}
C=e^{-2|(1-\eta)\alpha|^2},	
\end{align}
which rapidly asymptotes to zero for large $\alpha$ with any \mbox{$\eta<1$}, as shown in Fig.~\ref{fig:cat_decoherence}.

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{cat_decoherence}
	\caption{Coherence factor in an even-parity cat state subject to decoherence via loss, as a function of efficiency $\eta$, and the coherent amplitude $\alpha$.}\label{fig:cat_decoherence}
\end{figure}

>>>>

Consider a cat state (either even or odd parity), as per Eq.~(\ref{eq:cat_state_enc}). Subjecting this to a loss channel yields the mixed state,
\begin{align}
&\hat\rho_\mathrm{loss} = \mathcal{E}_\eta^\mathrm{loss}(\ket{\mathrm{cat}_\pm(\alpha)}\bra{\mathrm{cat}_\pm(\alpha)}) \nonumber\\
&= {\mathcal{N}_\pm}^2 [\mathcal{E}_\eta^\mathrm{loss}(\ket{\alpha}\bra{\alpha}) + \mathcal{E}_\eta^\mathrm{loss}(\ket{-\alpha}\bra{-\alpha}) \nonumber\\
&\pm \mathcal{E}_\eta^\mathrm{loss}(\ket{-\alpha}\bra{\alpha}) \pm \mathcal{E}_\eta^\mathrm{loss}(\ket{\alpha}\bra{-\alpha})]\nonumber\\
&= {\mathcal{N}_\pm}^2[\ket{\eta\alpha}\bra{\eta\alpha} + \ket{-\eta\alpha}\bra{-\eta\alpha}\nonumber\\
&\pm e^{-2|(1-\eta)\alpha|^2}(\ket{\eta\alpha}\bra{-\eta\alpha}+\ket{-\eta\alpha}\bra{\eta\alpha})].
\end{align}
Now it's evident that the off-diagonal terms (i.e those capturing coherence) accumulate a factor of,
\begin{align}
C=e^{-2|(1-\eta)\alpha|^2},
\end{align}
which rapidly asymptotes to zero for large $\alpha$ with any \mbox{$\eta<1$}, as shown in Fig.~\ref{fig:cat_decoherence}.

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{cat_decoherence}
	\caption{Coherence factor in a cat state subject to decoherence via loss, as a function of efficiency $\eta$, and coherent amplitude $\alpha$.}\label{fig:cat_decoherence}
\end{figure}
